\documentclass[11pt,letterpaper]{article}

\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

% Formatting
\pagestyle{empty}
\setlength{\parindent}{0pt}
\titleformat{\section}{\large\bfseries\scshape}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{12pt}{6pt}
\setlist[itemize]{leftmargin=1.5em, itemsep=2pt, parsep=0pt}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
}

\begin{document}

\begin{minipage}[t]{0.5\textwidth}
{\LARGE \textbf{Tom\'as E. Monarrez}}
\end{minipage}%
\begin{minipage}[t]{0.5\textwidth}
\raggedleft
\textbf{March 2026}
\end{minipage}

\vspace{4pt}

\section*{Contact Information}

Phone: (267) 990-7556 \\
Email: \href{mailto:tomas.monarrez@phil.frb.org}{tomas.monarrez@phil.frb.org} \\
Office: 10 N Independence Mall W, Philadelphia, PA, 19106 \\
Website: \href{https://tmonarrez.github.io}{tmonarrez.github.io}

\section*{Employment}

\begin{tabular}{lll}
Federal Reserve Bank of Philadelphia & 2023-- & Senior Research Fellow \\
U.S. Department of Education & 2023--2025 & Expert \\
U.S. Department of Education & 2021--2023 & Senior Advisor, Office of the Chief Economist \\
Urban Institute & 2020--2021 & Senior Research Associate \\
University of Maryland, College Park & 2019--2021 & Lecturer \\
Urban Institute & 2018--2020 & Research Associate \\
\end{tabular}

\section*{Education}

\begin{tabular}{lll}
University of California, Berkeley & 2012--2018 & Ph.D. in Economics (David Card, Jesse Rothstein, chairs) \\
University of Texas at Austin & 2007--2012 & B.A. in Economics and Mathematics (\textit{cum laude}) \\
\end{tabular}

\section*{Fields of Interest}

Labor Economics, Economics of Education, Urban Economics, Applied Econometrics

\section*{Published Research}

``The Effect of Student Loan Payment Burdens and Nonfinancial Frictions on Borrower Outcomes,'' joint with Lesley Turner. \textit{Review of Financial Studies}, Forthcoming.

\medskip

``Trends in Student Loan Repayment,'' joint with Rajeev Darolia and Lesley J. Turner. 2024. \textit{National Tax Journal}. Vol.~77(3): 681--710.

\medskip

``Dividing Lines: Racial Segregation Across Local Government Boundaries,'' joint with David Sch\"onholzer. 2023. \textit{Journal of Economic Literature}. Vol.~61(3): 863--87.

\medskip

``School Attendance Boundaries and the Segregation of Public Schools in the U.S.'' 2023. \textit{American Economic Journal: Applied Economics}. Vol.~15(3): 210--37.

\medskip

``The Effect of Charter Schools on School Segregation,'' joint with Brian Kisida and Matthew Chingos. 2022. \textit{American Economic Journal: Economic Policy}. Vol.~14(1): 301--40.

\section*{Working Papers}

``Shattered Metropolis: The Great Migration and the Fragmentation of Political Jurisdictions,'' joint with Jamie McCasland, David Sch\"onholzer, and Everett Stamm. 2025. \textit{Revision requested at American Economic Journal: Economic Policy.}

\medskip

``The Effect of the Great Recession on Student Loan Borrowing and Repayment,'' joint with Michel Grosz. 2025. \textit{Revision requested at Economics of Education Review.}

\medskip

``Using Centralized Lotteries to Measure the Effects of Universal Pre-K on Later Public Education Outcomes,'' joint with Breno Braga, Justin B. Doromal, Erica Greenberg, Leonardo Restrepo, and Rachel Lamb. \textit{AERA Education Policy}, Forthcoming.

\section*{Work in Progress}

``Boundaries in Motion: Effectiveness and Efficiency of School Redistricting,'' joint with David Sch\"onholzer and Yifei Wang.

\medskip

``Inequality in Student Loan Repayment by Race and Ethnicity,'' joint with Lesley Turner and Rajeev Darolia.

\medskip

``Fiscal, Demographic, and Academic Impacts of School District Secessions,'' joint with Barbara Biasi, Julien Lafortune, and David Sch\"onholzer.

\section*{Policy Reports}

``Student Loans for Graduate School: Who Will Be Affected by the New Federal Lending Limits?'' joint with Jordan Matsudaira and Dubravka Ritter. 2025. Federal Reserve Bank of Philadelphia.

\medskip

``CFI in Focus: Insights from Recent Research on Income-Contingent Student Loan Repayment,'' joint with Dubravka Ritter. 2024. Federal Reserve Bank of Philadelphia.

\medskip

``Special Four-Report Series on Student Loan Payments Resumption,'' joint with Dubravka Ritter. 2024. Consumer Finance Institute Special Report. Federal Reserve Bank of Philadelphia.

\medskip

``Back in the Loan Game: What Can We Expect from the Student Loan Payment Resumption?'' joint with Dubravka Ritter and Jacob Goldsmith. 2023. Consumer Finance Institute Report. Federal Reserve Bank of Philadelphia.

\medskip

``The Effects of Teacher Diversity on Hispanic Student Achievement in Texas,'' joint with Constance Lindsay. 2022. Urban Institute Research Report.

\medskip

``The Effect of State Higher Education Finance on College Enrollment and Degree Awards by Race.'' 2021. Urban Institute Research Report.

\medskip

``Can We Measure School Quality Using Publicly Available Data?'' joint with Matthew Chingos. 2020. Urban Institute Research Report.

\medskip

``Using Centralized Lotteries to Measure Preschool Impact.'' 2020. Urban Institute Research Report.

\medskip

``Measuring Differences in School-Level Spending for Various Student Groups.'' 2020. Urban Institute Research Report.

\medskip

``Does School Choice Make Segregation Better or Worse?'' joint with Matthew Chingos. 2020. Hoover Education Success Initiative Papers.

\medskip

``Racial and Ethnic Segregation within Colleges.'' 2020. Urban Institute Research Report.

\medskip

``Racial and Ethnic Representation in Postsecondary Education.'' 2019. Urban Institute Research Report.

\medskip

``The Effects of the Florida Tax Credit Scholarship Program on College Enrollment and Graduation,'' joint with Matthew Chingos and Daniel Kuehn. 2019. Urban Institute Research Report.

\section*{Fellowships, Awards, and Honors}

\begin{tabular}{ll}
2022 & Leadership for Educational Equity Fellow, United States Department of Education \\
2021 & Impact Fellow, Federation of American Scientists \\
2021 & President's Awards for Communications and Innovation, Urban Institute \\
2019 & Emerging Education Policy Scholar, Thomas B. Fordham Institute \\
2016 & Outstanding Graduate Student Instructor, UC Berkeley \\
2012 & Chancellor's Fellowship, UC Berkeley \\
& College of Liberal Arts Dean's Honor List, \textit{Cum Laude}, UT Austin \\
& College Scholar Award, Department of Mathematics, UT Austin \\
& Presidential Scholarship, UT Austin \\
& Longhorn Opportunity Scholarship, UT Austin \\
\end{tabular}

\section*{Invited Seminars and Presentations}

\textbf{2024} \quad American Economic Association Annual Meeting. NBER Economics of Education Program Meeting, Spring 2024. The Unfinished Legacy of Brown v.\ Board of Education at 70 Conference, Stanford University Educational Opportunity Project. AEFP Research Conference. Conference on Race, Racism, and Structural Inequality, Duke University Department of Economics. System Applied Micro Conference, Federal Reserve Bank of Chicago. CESifo Venice Summer Institute. BIG Student Loan Conference. NBER Summer Institute. APPAM Fall Research Conference.

\medskip

\textbf{2023} \quad Vanderbilt University Peabody College Leadership, Policy, and Organizations Colloquium Series. National Bureau of Economic Research Economics of Education Program Meeting, Spring 2023. Brookings Institution Higher Education Meeting Group. APPAM Fall Research Conference. Brown University Northeast Economics of Education Workshop.

\medskip

\textbf{2022} \quad American Economic Association, ASSA Annual Meeting. MIT Media Lab, Center for Constructive Communication.

\medskip

\textbf{2021} \quad U.S. Department of Housing and Urban Development. Race, Ethnicity, Gender, and Economic Justice Symposium, Yale University Economic Growth Center. Center on Education and Policy Analysis Seminar, Stanford University. Spencer Pre-K Lottery Conference, University of Michigan, Ford School of Public Policy.

\medskip

\textbf{2020} \quad Seminar Series, Federal Reserve Bank of Cleveland. Hoover Institution, Stanford University. American Economic Association, ASSA Annual Meeting (Poster Session). Washington Area Labor Economics Symposium, George Washington University.

\medskip

\textbf{2019} \quad APPAM 41st Annual Research Conference. Urban Affairs Association, 49th Annual Meeting. Truman School of Public Affairs Seminar, University of Missouri. School of Education Speaker Series, Saint Louis University. Graduate School of Education Seminar, University of Pennsylvania.

\medskip

\textbf{2018} \quad Workshop on Race and the Social Sciences, Yale University. AEFP 44th Annual Conference. The Modeling Group Brown Bag Seminar, Urban Institute.

\medskip

\textbf{2017} \quad Labor Economics Seminar (UC Berkeley). Labor Economics Symposium (UC Berkeley). Berkeley Evaluation and Assessment Research (BEAR) Seminar.

\medskip

\textbf{2016} \quad Center for Labor Economics, Labor Lunch (UC Berkeley). Political Economy Lunch (UC Berkeley).

\medskip

\textbf{2015} \quad Center for Effective Global Action, Development Lunch (UC Berkeley).

\section*{Referee Service}

\textit{American Economic Review: Insights} $\cdot$ \textit{American Economic Journal: Applied Economics} $\cdot$ \textit{Journal of Public Economics} $\cdot$ \textit{Economics of Education Review} $\cdot$ \textit{Econometrica} $\cdot$ \textit{Journal of Human Resources} $\cdot$ \textit{Review of Economics and Statistics} $\cdot$ \textit{Quarterly Journal of Economics}

\end{document}
